# Introduction {#intro}

This section will become the section for the administrative updates/organization once we have figured out how to use all of the bookdown features for our purposes.

The github repo corresponding to these pages is located at https://github.com/CSAFE-ISU/this-is-us

You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(intro). If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \@ref(glass).

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

````{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
````

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

````{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
````

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].  

# Guidelines for show and tell

A. What are the expectations from a spotlight presenter?

Spotlight presentations do not have to be full fledged presentations, but should aim to at least briefly address:
(1) Background of what the problem is
(2) What you have done
(3) What you are trying to do

B. What about the time constraint when there is more than one spotlight?

Given that there are at least two or at most three spotlights, you can take up as much time as you want in show and tell, as long as any other person presenting with you, gets at least the same amount of time as you. This means if you go first, you need to leave enough time for others too. If you have more material than the others then it's probably best that you go at the end.

It is encouraged that the spotlight presenters have a quick word amongst themselves as to who wants to go first, and who wants to go last.

C. Group Updates

There is no obligation to fill the whole time unless you want to, any group updates will come after all spotlight presentations and related discussions have finished and if there is enough time left.

D. What if I have to discuss ideas and want to practice for an upcoming big event presentation like a conference, seminar, creative component, or PhD defense etc?

Please schedule a talk in the reading/ working group which allows for deeper discussions and more time can be spent on different aspects of your research and presentation. You can set expectations from what kind of feedback you are expecting in the reading/ working group talk. The working group allows for a longer period of time to not only get valuable feedback but also ensures that other spotlight presenters are not feeling underwhelmed by the response to their work

